---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# socialsampler

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/socialsampler)](https://CRAN.R-project.org/package=socialsampler)
[![Codecov test coverage](https://codecov.io/gh/alexpghayes/socialsampler/branch/master/graph/badge.svg)](https://codecov.io/gh/alexpghayes/socialsampler?branch=master)
[![R build status](https://github.com/alexpghayes/socialsampler/workflows/R-CMD-check/badge.svg)](https://github.com/alexpghayes/socialsampler/actions)
<!-- badges: end -->

`socialsampler` extends [`rtweet`](https://rtweet.info/) to gracefully handle multiple tokens, to automatically use bearer tokens for increased sampling capacity, and to automatically retry failed API requests.

## Installation

You can install the development version of `socialsampler` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("alexpghayes/socialsampler")
```

## Sampling Twitter data with `socialsampler`

`socialsampler` provides (essentially) drop-in replacements for several `rtweet` functions. These drop-in functions follow the same naming conventions as `rtweet` functions, but with a `safe_*` prefix. For example:

```{r warning = FALSE}
library(socialsampler)

safe_get_friends("alexpghayes")
```

If you run into Twitter API rate limits, `socialsampler` will just wait for the rate limit to reset.

## Registering and managing your tokens

The major functionality of `socialsampler` is its ability to use multiple tokens for data collection, automatically using tokens with remaining API calls. Additionally, `socialsampler` uses both user tokens and bearer tokens. Again, this is automatic, and should at least double sampling capacity relative to `rtweet` for most API requests.

Registering a token is straightforward:

``` r
register_token(
  consumer_key = "FILL_THIS_IN",
  consumer_secret = "FILL_THIS_IN",
  access_token = "FILL_THIS_IN",
  access_secret = "FILL_THIS_IN"
)
```

You only ever need to register a token once, and `socialsampler` won't accidentally add any duplicate tokens to the token database. To see how many tokens you have, you can use:

```{r}
inspect_token_db()
```

You can import `rtweet` tokens into the database via `import_tokens_from_rtweet()`, and clear all tokens from the token database with `unregister_all_tokens()`.

If no tokens have been registered with `socialsampler`, API calls will look for a token registered with `rtweet` and use that token instead, again
automatically respecting rate limits and leveraging the corresponding bearer token. If you have not registered tokens either `socialsampler` or `rtweet` and you try to make an API request, you'll get an error.
